Security Properties for Stack Safety

### 2021-05-13 short/main.tex
Nit

To demonstrate the utility of our properties, we use them
to validate an existing mechanism, the
{\em stack-safety micro-policies} of~\citet{DBLP:conf/sp/RoesslerD18}, re-implemented
in the Coq proof assistant on top of a RISC-V specification. We
use QuickChick~\citep{Denes:VSL2014,Pierce:SF4}, a property-based testing
tool for Coq, to generate random programs and check
that Rossleer and Dehon's micro-policies correctly abort programs that
would violate stack safety.

>>>>

To demonstrate the utility of our properties, we use them
to evaluate an existing mechanism, the
{\em stack-safety micro-policies} of~\citet{DBLP:conf/sp/RoesslerD18}, re-implemented
in the Coq proof assistant on top of a RISC-V specification. We
use QuickChick~\citep{Denes:VSL2014,Pierce:SF4}, a property-based testing
tool for Coq, to generate random programs and check
that Rossleer and Dehon's micro-policies correctly abort programs that
would violate stack safety.
